---
title: "Benford"
output: pdf_document
author: "Angela Zhai, Zhaobin Liu, Yaotang Luo, Jiahao Xu"
date: "November 30, 2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(readr, readxl, data.table, tidyverse, benford.analysis, knitr)
```

# I. US 2010 Population Census Data

```{r echo=FALSE}
data(census.2000_2010) #gets data

cp <- benford(census.2000_2010$pop.2010, number.of.digit=2, sign="both") #generates benford object for 2010 population Census data in U.S. 

bfd.cp <- benford(census.2000_2010$pop.2010)
plot(bfd.cp)
```
The original data is in blue and the expected frequency according to Benford's law is in red.

Benford’s analysis of the first digits indicate the data basically follows Benford's Law.

Digit Distribution Second Order Test calculates the digit frequencies of the differences between the ordered (ranked) values in a data set. It shows that this dataset generally follows Benford's law, except some specific two digits.

The Chi-Square and Summation Difference plots almost fit Benford's law, but not good enough.

```{r echo=FALSE}
bfd.cp
```
Above result shows 5 largest discrepancies. As we can see from the plot, the highest deviation is 20.

From the log mantissa of the data, we can tell that the data follows Benford's Law. Because Mean closes to 0.5, Variance closes to 0.083, Ex. Kurtosis closes to -1.2, and Skewness closes to 0.

Degree of freedom equals 89 and p-value equals 0.6646, so failed to reject Benford's law. X-squared value equals 82.809 and closes to the value of degree of freedom, the distribution of this data set looks good. All in all, this dataset follows Benford's law.

The distortion factor is -0.781.

$~$ 

$~$ 

$~$ 

$~$ 

$~$ 

$~$ 

$~$ 
```{r echo=FALSE}
Bfd <- getBfd(cp)  #Gets the the statistics of the first Digits of a benford object.
#From this table, we can get the distribution of dataset by first two digits.
kable(Bfd[1:10, 1:6])
```

Table above shows the distribution of population data by first two digits.

```{r echo=FALSE}
# Show ten suspected two digits that contain most discrepancies from Benford's law.
kable(head(suspectsTable(cp),10))
```

Above table shows ten suspected two digits that contain most discrepancies from Benford's law.

```{r echo=FALSE}
suspects_ranked <- getSuspects(cp, select(census.2000_2010, -pop.2000)) #Gets the ’suspicious’ observations according to Benford’s Law.
kable(head(suspects_ranked, 10))
```

Table above gets the ’suspicious’ observations according to Benford’s Law. (Only shows 10 observations)

$~$


# II. NBA 2017-2018 Season Win Share
```{r echo=FALSE, message=FALSE}
season78 <- read_csv("season78.csv")
WS <- benford(season78$WS,number.of.digits = 2)
plot(WS)
```
The first plot shows that our data has the tendency to follow Benford's law. The chi-Squared Difference graph also has a very good-fit shape. 

```{r echo=FALSE}
WS
```
By the result, we can see the # of observation, # of obs for second order, and first digit analysed. The 5 largest deviations show that the smallest digit are 10 which follows the Benford's law as well. 

```{r echo=FALSE}
kable(head(suspectsTable(WS),10))
```

Above table shows the digits by decreasing order of discrepancies, and gets observations of the 2 most suspicious groups.

```{r echo=FALSE}
suspects <- getSuspects(WS, season78, how.many=2)
kable(head(suspects, 10))
```

Table above gets the ’suspicious’ observations according to Benford’s Law. (Only shows 10 observations)

```{r echo=FALSE}
#prints the duplicates by decreasing order
kable(head(duplicatesTable(WS), 10))
```

Above table shows the duplicates by decreasing order. There are 1167 observations with the most 2 duplicates values.
